An analysis of Lenin's work: Revolution, war, and fruta

### 2014-02-22 paper/distance.tex
Change name from Wn Analyzer to SynsetAnalyzer.
add new command for creating latex code to be included in the paper. remove brackets on wsd.tex

@@

% *WordnetAnalyzer
%   *Synset
%   *path, lch, wup
% *judge_word
% *judge_doc
% *judge_year
% Dado un conjunto de palabras, definimos la distancia de una palabra a este conjunto como 
%

\section{Results}
\subsection{Resultados sobre obras}
* Tabla de top words de Estado y Revolución
\begin{center}
  \begin{tabular}{ | l | l | l |}
    \hline
    \multicolumn{3}{|c|}{Top words for `State and Revolution'} \\ \hline
    \# & Word & Information Value \\ \hline

    1 & kautsky & 0.10 \\ \hline
    2 &  marx & 0.09 \\ \hline
    3 &  revolution & 0.09 \\ \hline
    4 &  works & 0.06 \\ \hline 
    5 & engels & 0.06 \\ \hline
    6 &  society & 0.06 \\ \hline
    7 & power & 0.05 \\ \hline
    8 &  party & 0.04 \\ \hline
    9 &  social & 0.04 \\ \hline
    10 &  experience & 0.03 \\ \hline 
    11 & bernstein & 0.03 \\ \hline
    12 &  question & 0.03 \\ \hline 
    13 & equality & 0.03 \\ \hline
    14 &  phase & 0.03 \\ \hline
    15 & 1917 & 0.03 \\ \hline
    16 & commune & 0.03 \\ \hline
    17 & one & 0.03 \\ \hline
    18 & republic & 0.03 \\ \hline
    19 & class & 0.02 \\ \hline
    20 & law & 0.02 \\ \hline
  \end{tabular}
\end{center}

\begin{center}
  \begin{tabular}{ | r |l |}
    \hline
    \multicolumn{2}{|c|}{$S_{dw}($`State and Revolution'$, w)$} \\ \hline
      $w$ & $S_{dw}(d, w)$ \\ \hline
      revolution &  0.177  \\ \hline
      power &  0.169  \\ \hline
      state &  0.154  \\ \hline
      commune &  0.133  \\ \hline
      republic &  0.123  \\ \hline
      politics &  0.118  \\ \hline
      music &  0.114  \\ \hline
      war &  0.110  \\ \hline
      philosophy &  0.094  \\ \hline
      idealism &  0.084  \\ \hline
      chicken &  0.092  \\ \hline
      computer &  0.082  \\ \hline
      mosquito &  0.044  \\ \hline
      lion &  0.059  \\ \hline
      alcohol &  0.067  \\ \hline
      toilette &  0.069  \\ \hline
  \end{tabular}
\end{center}

>>>>

\subsubsection{Word Sense Disambiguation}
\input{wsd}

\subsection{Top senses for given works}
\input{top_senses_the_state_and_revolution}
\input{top_senses_lenin_imperialism_the_highest_stage_of_capitalism}
\input{top_senses_lenin_materialism_and_empirio-criticism}
\input{top_senses_lenin_the_agrarian_programme_of_social-democracy_in_the_first_russian_revolution_1905-1907}
\input{top_senses_lenin_what_is_to_be_done?}

@@

% *SynsetAnalyzer
%   *Synset
%   *path, lch, wup
% *judge_word
% *judge_doc
% *judge_year
% Dado un conjunto de palabras, definimos la distancia de una palabra a este conjunto como 
%

### 2014-02-22 paper/wsd.tex
add new command for creating latex code to be included in the paper. remove brackets on wsd.tex

Our approach for WSD was a classical Lesk implementation that uses wordnet as a definition source with some tweaks.
Basically Lesk is based on the idea that words that co–occur in a sentence are being used to refer to the same topic.
The Lesk alghorithm{BIO} takes the word definition or gloss that we want to disambiguate and it compares it gloss against the glosses of the other words in the context.
Then a word is assigned that sense whose gloss shares the largest number of words in common with the glosses of the other words.
This algorhitm suffers the problem that relies on the word definition and definitions usually uses as less words as possible.
Not only that sometimes two different words, but related ones, uses no words in common in their definitions.
As we use the nltk wordnet we immediately notice an improvement using the rich set of relationships that Wordnet gives to us.
We added to Lesk word stems, hypernyms, hyponyms.
For the problem of short word description we modified the algorthim to use the definition of the word to disambiguate and to compare it against the context words directly.
Finally our algorithm chooses the best synset from wordnet based on the context words.

>>>>

Our approach for WSD was a classical Lesk implementation that uses wordnet as a definition source with some tweaks.
Basically Lesk is based on the idea that words that co–occur in a sentence are being used to refer to the same topic.
The Lesk alghorithm (BIO) takes the word definition or gloss that we want to disambiguate and it compares it gloss against the glosses of the other words in the context.
Then a word is assigned that sense whose gloss shares the largest number of words in common with the glosses of the other words.
This algorhitm suffers the problem that relies on the word definition and definitions usually uses as less words as possible.
Not only that sometimes two different words, but related ones, uses no words in common in their definitions.
As we use the nltk wordnet we immediately notice an improvement using the rich set of relationships that Wordnet gives to us.
We added to Lesk word stems, hypernyms, hyponyms.
For the problem of short word description we modified the algorthim to use the definition of the word to disambiguate and to compare it against the context words directly.
Finally our algorithm chooses the best synset from wordnet based on the context words.
